Surrogate Modelling of the Tritium Breeding Ratio

### 2020-05-29 elevator_pitch/elevator_pitch.tex
Elevator pitch updates

The tritium breeding ratio (TBR) is an essential quantity for the design of
modern and next-generation Tokamak nuclear fusion reactors. Representing the
ratio between tritium fuel generated in breeding blankets and fuel consumed
during reactor runtime, the TBR depends on reactor geometry and material
properties in a complex manner. In this work, we explored the
training of surrogate models to produce a cheap but high-quality approximation
for a Monte Carlo TBR model in use at the UK Atomic Energy Authority.

>>>>

The tritium breeding ratio (TBR) is an essential quantity for the design of
modern and next-generation Tokamak nuclear fusion reactors. Representing the
ratio between tritium fuel generated in breeding blankets and fuel consumed
during reactor runtime, the TBR depends on reactor geometry and material
properties in a complex manner. In this work, we explored the
training of surrogate models to produce a cheap but high-quality approximation
for a Monte Carlo (MC) TBR model in use at the UK Atomic Energy Authority.
